Computer Science House Constitution

### 2024-04-22 constitution.tex
I removed the two lines that are illegal (#224)
Co-authored-by: ikopke23 <144629825+ik6335@users.noreply.github.com>
300 i deleted socials in the table of abbreviations (#225)
* I removed the two lines that are illegal

* I think I deleted Socials when I put the table together but also I'm blaming Ella

---------

Co-authored-by: ikopke23 <144629825+ik6335@users.noreply.github.com>

\subsection{Abbreviations}
% Formatted as abbreviation  full term
\begin{tabular}{ l  l  l l l l}
	Chair   & \textit{Chairperson}            & Maintainer(s) & \textit{Constitutional Maintainer(s)} \\
	CSH     & \textit{Computer Science House} & OpComm        & \textit{Operational Communications}   \\
	E-Board & \textit{Executive Board}        & PR            & \textit{Public Relations}             \\
	Eval(s) & \textit{Evaluation(s)}          & R\&D          & \textit{Research and Development}     \\
	History & \textit{House History}          & ResLife       & \textit{Residence Life}               \\
	IMPs    & \textit{House Improvements}     & RTP(s)        & \textit{Root Type Person(s)}          \\
	Intro   & \textit{Introductory}                                                                   \\
\end{tabular}

@@

\asubsubsection{Qualifications for Chairperson, Evaluations Director, Social Director, Financial Director, Research and Development Director(s), House Improvements Director, History Director, Public Relations Director}
\begin{enumerate}
	\item Candidates must be Active Members during the term of office.
	\item Candidates must have at least one full semester of membership as an Active Member.
	\item Elected or selected candidates may not hold two simultaneous voting E-Board positions, and must therefore resign their current position or decline a second position should they be elected or selected to a second voting position.
	\item Candidates for Chair or Evals Director must reside on floor during the term of office.
\end{enumerate}

@@

\asubsubsection{Waiving of Qualifications}
\begin{enumerate}
	\item CSH may choose to waive the following subset of the qualifications for E-Board positions, as defined under \ref{Qualifications}, for all candidates:
	      \begin{enumerate}
		      \item Candidates must reside on floor during the term of office.
		      \item Candidates must have at least one full semester of membership as an Active Member.
		      \item Social and R\&D are the only voting E-Board positions that allow for dual directorship.
	      \end{enumerate}
	\item When a waiver is proposed, the Chair of the Vote shall state which E-Board position and qualification is being voted upon, and any nominated candidates not qualified under \ref{Qualifications} who would become qualified if the waiver passes.
	\item A Three-Quarters Immediate Vote with three-quarters quorum is then taken to determine whether the proposed waiver shall take effect.
	\item Each vote to waive a qualification must only apply to a single qualification for a single E-Board position.
	\item Waivers always apply to all candidates for the E-Board position.
\end{enumerate}

>>>>

\subsection{Abbreviations}
% Formatted as abbreviation  full term
\begin{tabular}{ l  l  l l l l}
	Chair   & \textit{Chairperson}            & Maintainer(s) & \textit{Constitutional Maintainer(s)} \\
	CSH     & \textit{Computer Science House} & OpComm        & \textit{Operational Communications}   \\
	E-Board & \textit{Executive Board}        & PR            & \textit{Public Relations}             \\
	Eval(s) & \textit{Evaluation(s)}          & R\&D          & \textit{Research and Development}     \\
	History & \textit{House History}          & ResLife       & \textit{Residence Life}               \\
	IMPs    & \textit{House Improvements}     & RTP(s)        & \textit{Root Type Person(s)}          \\
	Intro   & \textit{Introductory}           & Social        & \textit{Socials}                      \\                                  \\
\end{tabular}

@@

\asubsubsection{Qualifications for Chairperson, Evaluations Director, Social Director, Financial Director, Research and Development Director(s), House Improvements Director, History Director, Public Relations Director}
\begin{enumerate}
	\item Candidates must be Active Members during the term of office.
	\item Elected or selected candidates may not hold two simultaneous voting E-Board positions, and must therefore resign their current position or decline a second position should they be elected or selected to a second voting position.
	\item Candidates for Chair or Evals Director must reside on floor during the term of office.
\end{enumerate}

@@

\asubsubsection{Waiving of Qualifications}
\begin{enumerate}
	\item CSH may choose to waive the following subset of the qualifications for E-Board positions, as defined under \ref{Qualifications}, for all candidates:
	      \begin{enumerate}
		      \item Candidates must reside on floor during the term of office.
		      \item Social and R\&D are the only voting E-Board positions that allow for dual directorship.
	      \end{enumerate}
	\item When a waiver is proposed, the Chair of the Vote shall state which E-Board position and qualification is being voted upon, and any nominated candidates not qualified under \ref{Qualifications} who would become qualified if the waiver passes.
	\item A Three-Quarters Immediate Vote with three-quarters quorum is then taken to determine whether the proposed waiver shall take effect.
	\item Each vote to waive a qualification must only apply to a single qualification for a single E-Board position.
	\item Waivers always apply to all candidates for the E-Board position.
\end{enumerate}
